Nested sampling with multiple scalars

### 2015-08-20 Paper/ms.tex
Corner mass

>>>>

\section{A Diffusive Variant}
Have one walker, or a few (not a large number).

Explore the prior $\pi(\xx)$, and save sampled values of the scalars
(thinned, presumably). As a function of position $(s_1, s_2)$ there is a well
defined value of the cumulative prior mass
\begin{eqnarray}
M(s_1, s_2) &=& \int \pi(\xx)\mathds{1}\left(S_1(\xx) \leq s_1,
S_2(\xx) \leq s_2\right)\, d\xx
\end{eqnarray}
which can be approximated in a Monte Carlo fashion by
\begin{eqnarray}
\hat{M}(s_1, s_2) &=& \frac{1}{N}\sum_{i=1}^N \mathds{1}\left(S_1^i \leq s_1,
S_2^i \leq s_2\right)
\end{eqnarray}
